Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/discussions.tex

\paragraph{Smoothness of the value function.} In all of our proofs, $V^\pi$ is
assumed to be continuously differentiable for all $\pi$.  This %is a strong
hypothesis is not always satisfied in practice. Very simple environments
break this hypothesis, such as the pendulum swing-up environment,
with pendulum height as reward and torque as action.  Indeed, 
% assume that $\pi$
% is the optimal policy for the pendulum swing-up environment, with state
% representation $(\theta, \dot{\theta})$. 
the state space $(\theta, \dot{\theta})$ for this environment
can be partitioned into two subspaces $\mathcal{G}$ and $\mathcal{B}$, with
$\mathcal{G}$ the subspace where the optimal policy 
can swing up the pendulum without crossing the $y$-axis, and $\mathcal{B}$ where
it has to cross the $y$-axis. The difference of $V$-function between a point in
$\mathcal{G}$ and a point in $\mathcal{B}$ is lower bounded by a finite
quantity. 
%Besides, one can find two points $s_1 \in \mathcal{G}$ and $s_2 \in \mathcal{B}$
%such that $s_1$ and $s_2$ are arbitrarily close.
Consequently, $V^\pi$ is
discontinuous on the frontier between $\mathcal{G}$ and $\mathcal{B}$, which results in non infinitesimal advantages
for actions taken on the frontier. \TODO{Non infinitesimal advantages are found,
	more generally, as soon as a given policy has different regimes, depending on
	where it starts in state space. For such policies, at the frontier between two regimes,
the value function can be discontinuous, resulting in non infinitesimal advantages.}

\paragraph{Memory buffer size scalings}~Thm.~\ref{th:cont-params} is stated for
transitions sampled sequentially from a fixed infinite size sequence. In practice,
transitions are sampled from a memory buffer, to prevent excessive correlations.
The memory buffer used is a fixed size circular buffer, and is
filled with samples coming from a single infinite exploratory trajectory. In
our experiments, the same buffer size is used for all time discretization. When
$\deltat$ goes to $0$, this corresponds to learning nearly online on the
infinite sequence, since the buffer will only contain examples that are very
close temporally to the end of the sequence in physical time. While the resulting
algorithm \TODO{kind of} converges to a continuous time limit, it is still not
time discretization invariant, as the freshness of samples in the buffer will
vary with the time discretization.
A different choice would be to scale the size of the buffer by a factor of
$\frac{1}{\deltat}$. This would amount to always learning on the same physical time interval of
the trajectory. Our analysis, however, does not cover this case.

>>>>

\paragraph{Smoothness of the value function.} In all of our proofs, $V^\pi$ is
assumed to be continuously differentiable for all $\pi$.  This %is a strong
hypothesis is not always satisfied in practice. Very simple environments
break this hypothesis, such as the pendulum swing-up environment,
with pendulum height as reward and torque as action.  Indeed, 
% assume that $\pi$
% is the optimal policy for the pendulum swing-up environment, with state
% representation $(\theta, \dot{\theta})$. 
the state space $(\theta, \dot{\theta})$ for this environment
can be partitioned into two subspaces $\mathcal{G}$ and $\mathcal{B}$, with
$\mathcal{G}$ the subspace where the optimal policy 
can swing up the pendulum without crossing the $y$-axis, and $\mathcal{B}$ where
it has to cross the $y$-axis. The difference of $V$-function between a point in
$\mathcal{G}$ and a point in $\mathcal{B}$ is lower bounded by a finite
quantity. 
%Besides, one can find two points $s_1 \in \mathcal{G}$ and $s_2 \in \mathcal{B}$
%such that $s_1$ and $s_2$ are arbitrarily close.
Consequently, the value function is
discontinuous on the frontier between $\mathcal{G}$ and $\mathcal{B}$, which results in non infinitesimal advantages
for actions taken on the frontier. \TODO{Non infinitesimal advantages are found,
more generally, as soon as a given policy has different regimes depending on
where it starts in state space. For such policies the value
function is typically discontinuous at the frontier between two
regimes, resulting in non infinitesimal advantages. The
continuous-time DAU properties would only hold almost-everywhere.}

\paragraph{Memory buffer size scalings}~Thm.~\ref{th:cont-params} is stated for
transitions sampled sequentially from a fixed infinite size sequence. In practice,
transitions are sampled from a memory buffer, to prevent excessive correlations.
The memory buffer used is a fixed size circular buffer, filled
with samples from a single infinite exploratory trajectory. In
our experiments, the same buffer size is used for all time discretization. When
$\deltat$ goes to $0$, this corresponds to learning nearly online on the
infinite sequence, since the buffer will only contain examples that are very
close temporally to the end of the sequence in physical time. \TODO{this
contradicts the use of the buffer against correlations} While the resulting
algorithm converges to a continuous time limit, in the strictest sense it is not
time discretization invariant, as the freshness of samples in the buffer will
vary with the time discretization.
A different choice would be to scale the size of the buffer by a factor of
$\frac{1}{\deltat}$. This would amount to always learning on the same physical time interval of
the trajectory. Our theoretical analysis does not cover this case.
